\bf Classification and Regression on Random Dot Product Graphs

### 2025-01-24 draft.Rmd
minor updates

In figure \ref{fig:angle-regression-sim}, we compare algorithm \ref{alg:mlsm-fit} to fitting a regression model using graph transitivity and average degree of each vertex (scenario 1). 
Since this scenario is similar to a multilayer DCBM, we expect performance to be very similar, which is what we observe in the results. 
However, we cannot model this simulation as a multilayer DCBM since although each graph can be described as a DCBM, the graphs do not share the same vertex set. 
In figure \ref{fig:beta-regression-sim}, we see that linear regression using graph summary statistics performs better for smaller graphs, but as we draw more vertices, the ASE improves and so algorithm \ref{mlsm-fit} performs better, whereas graph summary statistics cannot improve with the number of vertices. 
Figures \ref{fig:theta-mse} and \ref{fig:beta-mse} show that the quasi-MLE estimators computed via algorithm \ref{alg:bezier-param-fit} are consistent.

@@

In the second example, we analyzed the larval *Drosophila* mushroom body connectome \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2020estimation}. 
This dataset consists of two graphs representing two networks of neurons, one for each hemisphere of the *Drosophila* brain. 
In these graphs, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
The number of neurons in each hemisphere is not equal (209 in the left hemisphere and 213 in the right hemisphere).
The resulting graphs are illustrated in figure \ref{fig:mbconnectome-graph}.

>>>>

In figure \ref{fig:angle-regression-sim}, we compare algorithm \ref{alg:mlsm-fit} to fitting a regression model using graph transitivity and average degree of each vertex (scenario 1). 
Since this scenario is similar to a multilayer DCBM, we expect performance to be very similar, which is what we observe in the results. 
However, we cannot model this simulation as a multilayer DCBM since although each graph can be described as a DCBM, the graphs do not share the same vertex set. 
In figure \ref{fig:beta-regression-sim}, we see that linear regression using graph summary statistics performs better for smaller graphs, but as we draw more vertices, the ASE improves and so algorithm \ref{alg:mlsm-fit} performs better, whereas graph summary statistics cannot improve with the number of vertices. 
Figures \ref{fig:theta-mse} and \ref{fig:beta-mse} show that the quasi-MLE estimators computed via algorithm \ref{alg:bezier-param-fit} are consistent.

@@

In this section, we apply \ref{alg:mslm-fit} to real data to see if we can extract estimates from the latent space that correspond to response variables. 
In the first example, we analyzed the larval *Drosophila* mushroom body connectome \citep{Eichler141762}, which has been studied as a GRDPG by \citet{athreya2020estimation}. 
This dataset consists of two graphs representing two networks of neurons, one for each hemisphere of the *Drosophila* brain. 
In these graphs, each vertex is a neuron, and the labels correspond to one of four neuron types (Kenyon Cells, Input Neurons, Output Neurons, and Projection Neurons). 
The number of neurons in each hemisphere is not equal (209 in the left hemisphere and 213 in the right hemisphere).
The resulting graphs are illustrated in figure \ref{fig:mbconnectome-graph}.

### 2025-01-24 draft.tex
minor changes
minor updates

In figure \ref{fig:angle-regression-sim}, we compare algorithm
\ref{alg:mlsm-fit} to fitting a regression model using graph
transitivity and average degree of each vertex (scenario 1). Since this
scenario is similar to a multilayer DCBM, we expect performance to be
very similar, which is what we observe in the results. However, we
cannot model this simulation as a multilayer DCBM since although each
graph can be described as a DCBM, the graphs do not share the same
vertex set. In figure \ref{fig:beta-regression-sim}, we see that linear
regression using graph summary statistics performs better for smaller
graphs, but as we draw more vertices, the ASE improves and so algorithm
\ref{mlsm-fit} performs better, whereas graph summary statistics cannot
improve with the number of vertices. Figures \ref{fig:theta-mse} and
\ref{fig:beta-mse} show that the quasi-MLE estimators computed via
algorithm \ref{alg:bezier-param-fit} are consistent.

@@

@@

In the second example, we analyzed the larval \emph{Drosophila} mushroom
body connectome \citep{Eichler141762}, which has been studied as a GRDPG
by \citet{athreya2020estimation}. This dataset consists of two graphs
representing two networks of neurons, one for each hemisphere of the
\emph{Drosophila} brain. In these graphs, each vertex is a neuron, and
the labels correspond to one of four neuron types (Kenyon Cells, Input
Neurons, Output Neurons, and Projection Neurons). The number of neurons
in each hemisphere is not equal (209 in the left hemisphere and 213 in
the right hemisphere). The resulting graphs are illustrated in figure
\ref{fig:mbconnectome-graph}.

>>>>

@@

In figure \ref{fig:angle-regression-sim}, we compare algorithm
\ref{alg:mlsm-fit} to fitting a regression model using graph
transitivity and average degree of each vertex (scenario 1). Since this
scenario is similar to a multilayer DCBM, we expect performance to be
very similar, which is what we observe in the results. However, we
cannot model this simulation as a multilayer DCBM since although each
graph can be described as a DCBM, the graphs do not share the same
vertex set. In figure \ref{fig:beta-regression-sim}, we see that linear
regression using graph summary statistics performs better for smaller
graphs, but as we draw more vertices, the ASE improves and so algorithm
\ref{alg:mlsm-fit} performs better, whereas graph summary statistics
cannot improve with the number of vertices. Figures \ref{fig:theta-mse}
and \ref{fig:beta-mse} show that the quasi-MLE estimators computed via
algorithm \ref{alg:bezier-param-fit} are consistent.

@@

In this section, we apply \ref{alg:mslm-fit} to real data to see if we
can extract estimates from the latent space that correspond to response
variables. In the first example, we analyzed the larval
\emph{Drosophila} mushroom body connectome \citep{Eichler141762}, which
has been studied as a GRDPG by \citet{athreya2020estimation}. This
dataset consists of two graphs representing two networks of neurons, one
for each hemisphere of the \emph{Drosophila} brain. In these graphs,
each vertex is a neuron, and the labels correspond to one of four neuron
types (Kenyon Cells, Input Neurons, Output Neurons, and Projection
Neurons). The number of neurons in each hemisphere is not equal (209 in
the left hemisphere and 213 in the right hemisphere). The resulting
graphs are illustrated in figure \ref{fig:mbconnectome-graph}.
